\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Muhammad Hasan Suriya} \\ \vspace{1pt}
    Ottawa, Canada \ \ \
    \raisebox{-0.1\height}\faPhone\ +1 (343) 551-9777 \ \textbullet \
    \href{mailto:mhsuriya.w@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{mhsuriya.w@gmail.com}} \\
    \href{https://linkedin.com/in/muhammad-hasan-suriya/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/muhammad-hasan-suriya}} ~
    \href{https://github.com/mhasansuriya}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/mhasansuriya}} \\
    \vspace{-8pt}
\end{center}



%-----------EDUCATION-----------

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
    {Carleton University}{Sep. 2020 -- Apr 2026}
    {Bachelor of Engineering in Computer Systems Engineering}{Ottawa, Canada}
\resumeItemListStart
    \resumeItem{Current Courses: Program Project, Computer System Design, Real-Time Operating Systems}
    \resumeItem{Certifications: Microsoft - Foundational C\#, Security, Compliance \& Identity Fundamentals (in progress); Google Cloud - Generative AI Courses; FreeCodeCamp - Responsive Web Design }
\resumeItemListEnd
\resumeSubHeadingListEnd

%----------- SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, Java, Python, HTML/CSS, Javascript} \\
     \textbf{Developer Tools}{: Linux, Git, MATLAB, Blender, VS Code} }}
\end{itemize}
\vspace{-16pt}


%-----------PROJECTS-----------
\section{Projects}
\vspace{-5pt}
\resumeSubHeadingListStart

\resumeProjectHeading
    {\textbf{Interactive Tabletop System} $|$ \emph{Embedded Systems, Python, Web Development}}{January 2025 – Present}
    \resumeItemListStart
        \resumeItem{Developing an interactive tabletop environment for Dungeons \& Dragons players, integrating touchscreen controls, audio/visual systems, and real-time map rendering using a Raspberry Pi 4.}
        \resumeItem{Created a web server backend to manage and store maps, player data, and environment presets, allowing seamless control via a custom-built touchscreen interface.}
        \resumeItem{Integrated sensors, audio outputs, and dynamic lighting effects to simulate immersive in-game environments.}
        \resumeItem{Showcased skills in embedded systems design, software-hardware integration, web development, and real-time system control.}
    \resumeItemListEnd
\vspace{-13pt}

\resumeProjectHeading
    {\textbf{Task Manager – Client-Server System} $|$ \emph{C/C++}}{ October 2024 – January 2024}
    \resumeItemListStart
        \resumeItem{Implemented a real-time, concurrent task execution system using UDP sockets to support multiple clients simultaneously.}\vspace{-13pt}
        \resumeItem{Designed priority-based task scheduling and logging, ensuring efficient data transmission, resource management, and concurrency using multi-threading.}
        \resumeItem{Demonstrated strong systems programming skills (memory handling, threading, and network communication).}
    \resumeItemListEnd
\vspace{-13pt}

\resumeProjectHeading
    {\textbf{Macro Tracking Logger} $|$ \emph{Python}}{January 2024 - May 2024}
    \resumeItemListStart
        \resumeItem{Developed a simple executable application that logs daily macro inputs (carbs, protein, fat, calories) into a text file with date-stamped entries.}
        \resumeItem{Used Python for file handling, user input validation, and formatted logging to ensure easy tracking and analysis.}
        \resumeItem{Focused on clean user experience, ensuring inputs are appended automatically without manual file management.}
    \resumeItemListEnd
\vspace{-13pt}

\resumeProjectHeading
    {\textbf{GPA Management Systems} $|$ \emph{C \& C\#}}{June 2023 – August 2023}
    \resumeItemListStart
        \resumeItem{Developed student record and GPA calculation systems in both C and C\#, focusing on strengthening foundational programming knowledge.}
        \resumeItem{Built the C version as a command-line tool using linked lists for dynamic memory management, incorporating course handling, GPA calculation, and sorting functionalities.}
        \resumeItem{Created a C\# console application using Dictionaries and Lists to calculate GPA, dynamically assigning letter grades and summarizing student performance.}
    \resumeItemListEnd
\vspace{-13pt}

\resumeSubHeadingListEnd
\vspace{1pt}


%-----------EXTRACURRICULAR ACTIVITIES---------------
\section{Extracurricular Activities}
\resumeSubHeadingListStart
    \resumeSubheading{Carleton University Muslim Students' Association (CUMSA)}{Winter 2023 -- Winter 2025}{IAW Planning Team, VP External}{}
        \resumeItemListStart
            \resumeItem{Acquired and managed funds for Islam Awareness Week 2024, ensuring sponsorship acquisition, along with successful budgeting and fundraising over the course of the event}
            \resumeItem{Organized various other events for Islamic History Month, Charity Week, and some advocacy events}
            \resumeItem{Managed the communications and public relations for the organization}
        \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------HOBBIES---------------
\section{Hobbies}
\resumeSubHeadingListStart
    \resumeItemListStart
        \resumeItem{Football, Running, Swimming, Skiing, Cycling}
        \resumeItem{Worldbuilding and designing systems for fictional settings to create functional worlds}
    \resumeItemListEnd
\resumeSubHeadingListEnd
  
\end{document}

